NMRlipids IV: Other than PC headgroups

### 2017-02-21 Manuscript/manuscript.tex
Updates

@@

\todo{Simulation data for lipids with different headgroups to be collected}

@@

In addition to the changes in PC headgroup order parameters with 
ion binding, also changes in PS and PG headgroup order parameters
are measured.
\todo{Add this data}.

>>>>

Based on superficial reading, the conclusions in the literature are roughly
1) glycerol backbone structures are largely similar irrespectively of the headroup \cite{gally81},
2) glycerol backbone and headgroup strucures are similar in model membranes and in bacteria \cite{gally81,??},
3) headgroup structure is phosphatidylserine more rigid than in other phospholipids, which are quite similar to
each others \cite{??}.
In contrast to PC lipids, extensive discussion on glycerol backbone and headgroup structural details do not
exist (as far as I know).

@@

Several simulations containing PE, PG and PS lipids have been published \cite{??},
however, glycerol backbone and headgroup order parameters are not compared to
the experiments (based on superficial reading of literature).

Glycerol backbone and headgroup order parameters for PS lipids from experiments
and simulations are shown in Fig. \ref{HGorderParametersPOPS}.
The preliminary test with CHARMM GUI simulations show suggest that the model
overestimates magnitudes in $\beta$ and g$_3$ order parameters and forking in $\alpha$.
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPS.eps}
  \caption{\label{HGorderParametersPOPS}
    Order parameters for POPS headgroup and glycerol backbone from simulations and experiments without CaCl$_2$ 
    (DOPS from \cite{browning80} contains 0.1M of NaCl, POPC:POPS mixture from \cite{roux90}).
    Absolute values are shown for experimental data, because signs are not known.
    Simulations values are -S$_{CH}$
  }
  \todo{More simulation data for lipids with different headgroups to be collected}
  \todo{CHARMM GUI simulation contains only counter ions as potassium.
    All experiments here contain some amount of sodium salt. The best
    ion concentrations for comparison should be figured out.}
  \todo{Experimental signs of the order parameters would highly useful.}
\end{figure}

@@

In addition to the changes in PC headgroup order parameters with 
ion binding, also changes in PS and PG headgroup order parameters
are measured.

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/PSPGwithCaCl.eps}
  \caption{\label{PSPGchangesWITHCaCl}
    Changes in order parameters
  }
  \todo{Get the small concentration data from the inserts}
\end{figure}
